\graphicspath{{Implementation/Figures/}}
\chapter{Implementation}
\section{Implementation}
\label{S:1}
For analysing citation dataset, a treasure trove of openly accessible citation related information of research publications are nowadays available. They are considered as relics of scholarly communication representing the trend of previously published works as to how they were referred to by the citing authors. As the Web is becoming more and more innovative and influential medium for scientific communication, citation analysis and other bibliometric practices have found some major applications in studying this new phenomenon in scholarly communication.\\

We crawled a massive publication dataset of Computer Science field from one of the largest archived datasets, Microsoft Academic Search (MAS). Initially, rank list given by the MAS was used to obtain the list of respective paper Ids. The paper Ids, thus obtained, were then used to fetch all the data and required credentials of the publications. In order to avoid overloading of a particular server with spurting traffic, we distributed the crawling to different systems using Tor. We crawled information related to 6 million papers. For efficient browsing and extraction, an exponential back-off time was devised to send request again in case of server or connection failure. From the perspective of both client and server, robot restrictions imposed by the servers were strictly followed for avoiding any disruption in efficient crawling of data.\\

The extracted dataset had several inconsistencies that was removed by using a series of steps. We have filtered the dataset as per requirement of our study by removing all such papers that had insufficient bibliographic attributes such as unique paper index, publication venue, list of authors, publication year, valid references etc. Also, we have filtered out some of the forward citations; i.e., citations to the papers which got published after the publication of the citing paper. We have considered papers published in the year ranging between 1859 and 2012 that have at least one incoming or outgoing citation, i.e., all the disconnected nodes with zero in-degree and zero out-degree are removed. The filtered dataset now contains around 5 million papers. Some of the references that point to papers but not cited (swaying references) are also removed.\\

For instance, searching with the paper title we only found roughly 88.12\% of the papers which can be identified with their respective research fields. Remaining (11.88\%) of the papers were added using publication journal ID of the paper. More than 19 million authors from diverse research domains and 38 million papers are weekly updated in MAS. In each field, on an average ten-year impact indicates the average number of citations that each individual paper within a field received from the papers of other fields during the years 1859 to 2012 are collected. Fig. 5.1 highlights year-wise growth pattern of the various items in the dataset. Overall, we analyse a large scale dataset to strengthen the claims we have made in our paper.
\section{Terminologies}
\label{S:2}
Here we define the terminologies used throughout the paper.\\

\textbf{Publication age:} Publication age refers to the difference between the years when a paper has collected its last citation to its original publication year.\\

\textbf{Citation age:} Citation age refers to the total count of productive years, i.e., we consider only those years when paper has received at least one annual citation during its effective publication age.\\

\textbf{Attachment rate}: It gives a close probability that a new article is most likely to cite a paper which has already received k number of citations. Attachment rate acts as a significant parameter to model the growth of citations in different time windows leading to traditional cumulative advantage models.\\

\textbf{Sleeping beauty:} It refers to those papers which has remained unrecognised for a long period known as ‘Hibernation period’ and then, almost suddenly started to collect huge volume of citations by another weighted article. The threshold is set as papers which were published before 1960, have received more than 250 citations and a ratio of average citation age to publication age of greater than 0.7.\\

\textbf{Discovery papers:} Papers that received more than 500 citations and a ratio of average citation age to publication age of less than 0.4 are classified under Discovery publications. Such papers exhibit an increased citation count (k) in a very short average citation age.\\

\textbf{Hot papers:} We define hot papers as those papers which received greater than 1500 citations and whose ratio of average citation age to publication age is greater than 23.\\

The heuristics that we follow for peak detection, we first try to find the potential peak (by normalizing each point by the maximum citation value) accounted for the papers. The two conditions that need to be satisfied are – (i) First, we consider only those years whose citations are greater than or equal to 60\% of the maximum citation (max. Peak) received by each paper. (ii) Then, we calculate the potential peaks i.e., the years which have more than 2 years of gap.\\
\textbf{Limitations:} In case, a situation is encountered where condition (i) is satisfied but for condition (ii) the consecutive gap is less than 2 years; we then, treat it as a single peak and consider the last year as the time of peak. Next, we categorize papers into either single peak or multiple peak. We define the citation trajectories into five different categories :–\\
\begin{itemize}
    \item \textbf{Early peak (early):} Papers whose trajectory depicts a single peak and which received its maximum citation peak within the initial five years excluding the first year after publication followed by a sharp fall. Moreover, the paper should receive at least one citation per year throughout its effective publication age. This condition is referred to as l-condition.
    \item \textbf{Late peak (late):} Papers that collect few or no citations in the initial years and then, it rises to a single peak in the duration of at least five years after publication (excluding the fifth year) are categorized into late peak rising paper. It should satisfy the l-condition also.
    \item \textbf{Monotonically increasing (moninc):} Papers which satisfy the l-condition and for which the citation count gets accumulated monotonically increasing starting from the year of publication until its effective publication age with sufficient volume of citations before the occurrence of peak.
    \item \textbf{Monotonically decreasing (mondec):} Papers which got single peak in the immediate next year after publication followed by a sharp decay of citations with sufficient volume of citations collected after occurrence of the peak depicts monotonically decreasing curve. It further, should also satisfy the l-condition.
    \item \textbf{Multiple peaks (multi):} Papers that experience multiple peaks at different time points i.e., peaks occurring with a gap of more than two years and satisfying the l-condition fall under this category.
\end{itemize}

\section{Analysis of Dataset}
As per our analysis over the dataset, we have found the following details:
\begin{center}
    \begin{tabular}{|c|c|}
        \hline
         Total number of papers & 1,269,909,021 \\
         \hline
         Number of Conference Papers & 75,008,519\\
         \hline
         Number of Journal Papers & 51,900,106\\
         \hline
         Number of Conference Papers & 75,008,519\\
         \hline
         Number of conferences with at least one citation & 598203\\        
         \hline
         Number of journal papers with at least one citation & 490249\\
         \hline
         Number of Citations & 528,682,289\\
         \hline
         Number of authors per paper & 0.9037\\
         \hline
         Number of papers per author & 1.1064\\
        \hline
    \end{tabular}
\end{center}

The extracted dataset had several inconsistencies that was removed by using a series of steps. We have filtered the dataset as per requirement of our study by removing all such papers that had insufficient bibliographic attributes such as unique paper index, publication venue, list of authors, publication year, valid references etc. Also, we have filtered out some of the forward citations; i.e., citations to the papers which got published after the publication of the citing paper. We have considered papers published in the year ranging between 1859 to 2012 that have at least one incoming or outgoing citation, i.e., all the disconnected nodes with zero in-degree and zero out-degree are removed. The filtered dataset now contains around 5 million papers. Some of the references that point to papers but not cited (swaying references) are also removed. Above table provides some of the salient features of the obtained dataset.\\
Dataset characteristics- Growth of citation, author and paper count over time. X-axis denotes the years in which citations have been accounted whereas Y-axis denotes count of authors, papers and citations per year.
\section{The Preferential Attachment Model}

Preferential attachment model highlights the well-established fact in scientific community that papers which have high incoming citation history are the ones most likely to be cited again in the near future than the less-cited publications. As a result, we can conclude that the probability for an ith paper to receive a citation again is directly proportional to the total citation count ci that a paper has managed to collect in its effective past citation age. To measure the attachment rate, we consider the following:
\begin{itemize}
    \item Citation count (k) for a paper in a given time frame.
    \item  Number of times each paper with a given citation count (k) was subsequently cited in another time window.
\end{itemize}

The observation reveals that the value of attachment rate (Ak) is a nearly linear function for k less than 150. The log-normal behavior of graph arises from a nearly linear preferential rate given by Ak = k/(1+alnk), where a is positive integer. The graph refers to the fact that Ak might be increasing slightly faster than linearly with respect to k. Computer Science domain has evolved in architecture and application from the early 2000. Due to increased exposure to digital platforms and increased paper’s visibility in applied research domains, the attachment rate for the year range 2000-2009 has shown a significant increase when compared with other attachment rates. However, linear preferential attachment rate is concluded with the following limitations – 
\begin{itemize}
    \item Linear rate usually implies power-law form of growth; but we observe a log-normal form of distribution in our study.
    \item It fails to predict the dynamics of citation bumps or sudden evolution of individual papers.
    \item It does not take into account the fact that the probability of incoming citations varies as a function of time.
\end{itemize}

The attachment rate - The attachment rate Ak versus the number of citations k, especially for k less than 150 is being represented in a log-log scale. Different colors depicts the change in k for different year ranges. Here Ak is a nearly-linear function, i.e., as the citation count increases along the x-axis, attachment rate rises almost linearly till k < 150. After comparison, it shows that the slope of line depicting the year range 2000-2009 is slightly steeper than the same for other year ranges. Also, we observe that the cumulative advantage models do not take into account the regularity of citations received as well as the fact that the probability of incoming citations also varies as a function of time. We find that the probability of citation decays after receiving maximum citation in an initial growth phase, but here in this model, an older paper continues to collect citations irrespective of its age.
\\\\\\\\\\\\\\\\\\\\
\begin{document}
\\
\begin{center}
    \large \textbf{RESULT}
\end{center}
Raw citation count is a determinant of a paper’s acceptability and significance in a scientific community. A comprehensive citation analysis of Computer Science domain covering 2,101,548 out of a total of 11,971,250 citations from the year 1859 to 2012 is performed. We bring out an extensive study on citation histories of highly-cited and significant papers in Computer Science domain which exhibits unique citation activity over its effective lifetime. Generalized work on identifying the hot publications and major breakthrough discovery papers considering 110 years of data of physical review journals is done earlier by Render. Here, we explore similar patterns in Computer Science domain to expand such analysis. In addition, in each individual category, we study the impact of journals/conferences with the changing dynamics of citations. Further, this also helps us to examine how the Computer Science field has evolved in architecture and application over the years. We also try to extend our analysis by re-defining and profiling the activity of hot publications of Computer Science domain individually into five citation trajectories – a peak in the initial years after publication (early), a peak detected in the late years of its effective lifetime (late), multiple peaks (multi), multiple peaks monotonically increasing (moninc) and multiple peaks monotonically decreasing (mondec). Identifying the behaviour exhibited by the ‘Sleeping Beauties’ of Computer Science, we find that such papers exhibit highest single peak, but at much later years of its total publication age. Thus, precise predictability of citation based measures is necessary to determine the quality of publications gauging impact factors of various scientific players.
\end{document}
\begin{document}
\\
\begin{center}
    \large \textbf{CONCLUSION}
\end{center}
Citation is a spontaneous process where, degree of excursus is not directly determinable. Several factors play along in its manipulation. Here, we detected bi-directional patterns and tried to understand the intention behind such sudden superfluous outflow in citations. It is found that mostly such patterns are field specific and highlights intrinsic property of a publication house to mutually uplift performance of all its journals. Though, a rapid increase in publication count inflating impact factor of its associate journal is a possible indication towards anomaly. Such grouping in journal-journal citation network is influenced by underlying editor co-authorship networks, author-author collaboration networks and a multilayer approach to take into account all such possible reasons.
\end{document}